Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-11-07 hazelnut-popl17.tex
Fixed #19

Hazelnut is not intended as an end-user tool itself. Instead, it serves as a foundational account of typed structure
editing. To that end, we describe how
Hazelnut's rich metatheory, which we have mechanized using the Agda proof assistant, serves as a guide when we extend the calculus to include binary sum types. We also discuss various interpretations of holes, and in so doing
reveal connections with gradual typing and contextual modal type theory
(the Curry-Howard interpretation of contextual modal logic.) Finally, we
discuss how Hazelnut's semantics lends itself to implementation as an event-based functional reactive program. Our simple reference implementation is written in OCaml and compiled using \lstinline{js_of_ocaml}.

>>>>

Hazelnut is not intended as an end-user tool itself. Instead, it serves as a foundational account of typed structure
editing. To that end, we describe how
Hazelnut's rich metatheory, which we have mechanized using the Agda proof assistant, serves as a guide when we extend the calculus to include binary sum types. We also discuss various interpretations of holes, and in so doing
reveal connections with gradual typing and contextual modal type theory, the Curry-Howard interpretation of contextual modal logic. Finally, we
discuss how Hazelnut's semantics lends itself to implementation as an event-based functional reactive program. Our simple reference implementation is written in OCaml and compiled using \lstinline{js_of_ocaml}.
